---
title: "data.table Practice Note"
author: "EuniCheng"
date: "2018/4/5"
output: html_document
---
Source: [DataScienceRBook 7.2](https://yijutseng.github.io/DataScienceRBook/eda.html#datatable)

<style>
pre code, pre, code {
  white-space: pre !important;
  overflow-x: scroll !important;
  word-break: keep-all !important;
  word-wrap: initial !important;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## dplyr Function 統整
- `selsec()`
- `filter()`
- `mutate()`
- `summerise()`：計算統計值
- `group_by`
- `arrange`:排序
- `rename`

##

```{r}
library(dplyr)
library(SportsAnalytics)

NBA <- fetch_NBAPlayerStatistics()
```

### 語法

```{r results="hide"}
DT[Position=='C',.(Num=.N,ThreeMadeMean=mean(ThreesMade)),by=Team]
```

用 `filter()` 選擇 Team 為 "BOS" 或 "SAN" 
```{r results="hide"}
filter1 <- filter(NBA$Team %in% c("BOS","SAN"))
```

`filter()` 與 `summarise()` 合併使用：<br>
找出**出場數>60的人**的球員**個數**、**不重複的隊伍數**以及**不重複的守備位置數**
```{r results="hide"}
filter1 <- filter(NBA$GamePlayer>60) %>%
  summarise(nPlayer=n(), nTeam=n_distinct(Team), nPosition=N_distinct(Position))
```

`group_by()`像是計算**各隊****各守備位置**的球員數、平均出場數
```{r results="hide"}
group1 <- group_by(NBA,Team,Position) %>%
  summarise(nPlayer=n(),meanPlayed=mean(GamePlayed))
```

`arrange`:資料計算完後排序
```{r results="hide"}
ascending <- arrange(NBA,GamePlayed)
descending <- arrange(NBA,desc(GamePlayed))
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
